Team size and composition in home health care

### 2023-10-25 paper-presentation/paper-presentation.qmd
Minor

For some grade of service [$\gamma$]{style="color: red;"}, the required weekly capacity [$C$]{style="color: red;"} is $$C = \rho + \gamma z \rho$$

where [$\rho$]{style="color: red;"} $= m_am_sm_g$ is the average demand, and [$z$]{style="color: red;"} is the peakedness given by $$z = \frac{\sigma_g^2}{m_g} + m_g + m_g(1−G_s)(\frac{\sigma_a^2}{m_a}-1)$$
Hence, the utilization of the capacity [$C$]{style="color: red;"} is $$\frac{\mathbb{E}[N]}{C} = \frac{1}{1 + \frac{\gamma\sqrt{z}}{\sqrt{\rho}}}$$

>>>>

::: {.r-fit-text}
For some grade of service [$\gamma$]{style="color: red;"}, the required weekly capacity [$C$]{style="color: red;"} is $$C = \rho + \gamma z \rho$$

where [$\rho$]{style="color: red;"} $= m_am_sm_g$ is the average demand, and [$z$]{style="color: red;"} is the peakedness given by $$z = \frac{\sigma_g^2}{m_g} + m_g + m_g(1−G_s)(\frac{\sigma_a^2}{m_a}-1)$$
Hence, the utilization of the capacity [$C$]{style="color: red;"} is $$\frac{\mathbb{E}[N]}{C} = \frac{1}{1 + \frac{\gamma\sqrt{z}}{\sqrt{\rho}}}$$
:::
